\input{preamble}

\begin{document}

% Use roman numbers on the start of the report
\pagenumbering{Roman}
% Use plain style
\thispagestyle{plain}

% Title page
\input{title_page}

% Create table of contents
\setcounter{secnumdepth}{2} % set numbering depth of sections and chapters
\setcounter{tocdepth}{2} % set numbering depth of table of contents
\addcontentsline{toc}{chapter}{Table of Contents}
\tableofcontents*

% Use temporary line numbers on all pages
\setpagewiselinenumbers
\modulolinenumbers[5]
\linenumbers

% Main Contents of report, add chapters here
\chapter{Introduction}
\pagenumbering{arabic}
\input{introduction}

\chapter{Background and Literature Review}
\input{bg/bg_intro}
\input{bg/concurrency}
\input{bg/ruby}
\input{bg/tcp_http}
\input{bg/web_servers}
\input{bg/literature_review}
\input{bg/development_method}

\chapter{Analysis and Design}
\meta{Should describe how and why I have decided upon the set of requirements.
  Given my choice of development method, there is not much design upfront,
        hence this section will only contain some initial thoughts on the
          structure of the software.}
\input{analysis/requirements_specification}
\input{design/design}

\chapter{Implementation and Testing}
\input{implementation/implementation}
\meta{I choose to put imlementation and testing together as that suits the
  development method well. The chapter will contain interesting parts of the
    implementation, problems which arised along the way and how I solved them.
There is a section fore each of the requirements.}
\section{HTTP Parser}
\meta{describe how the parser works and the alternatives considered}
\section{Logging}
\meta{describe the logging functionality (possibly not interesting and might
    be skipped)}
\section{Concurrency}
\meta{describe the concurrency model and the differnt iterations}
\section{Static and Dynamic files}
\meta{Describe how static and dynamic files are served}
\section{Rack Interface}
\meta{describe how the Rack interface was implemented and what it required}

\chapter{Demonstration and Evaluation}
\meta{Demonstrate the final product with screenshots and describe how is is
  used. This section will also contain the results of the benchmarks. The
    evaluation will look back on the requirements and see whether they have
    been fulfilled.}
\section{Demonstration}
\meta{Briefly show screenshots and how the server works and is distributed}
\section{Benchmarks}
\meta{Show the results of benchmarking the server with various Ruby Vm's. The
results will also be analyzed to find the source of possible bottlenecks and
also compared to other webservers.}

\chapter{Conclusion}
\input{conclusion}


\label{theend}

% Bibliography 
\bibliographystyle{plain}
\bibliography{references/Thesis}
\nocite{*}
\label{bib}

% Appendix
\appendix
\appendixpage
\input{acceptance_tests}

\label{pagecount}

\newpage
\listoffixmes
\addcontentsline{toc}{chapter}{Todo}

\end{document}
