\section{System overview}
% \meta{The system as a whole. How it works with diagrams}

%intro
The user interface with Yarn through a Ruby script which accepts a
hostname and port number for to listen for incoming requests on, the number
of processes to fork and a Rack file. All parameters are optional, and default
values are used if none are given. By default the webserver will listen on
\texttt{127.0.0.1:3000}, with four worker processes serving static and dynamic
content. If a Rack file is given, then Yarn will serve requests by invoking
the Rack application. For debugging purposes, the user can supply a parameter
to include debug messages in the log. The following describes how Yarn handles
requests when serving static and dynamic files, and then how it serves Rack
applications.

When Yarn is started it will create a TCP server that listens for connections
on either the given or default port and hostname. If a Rack file is given,
then the application will be loaded. Then the process will fork into the given
number of workers and Yarn is ready to handle incoming requests. Each worker
contains a loop which, when registering an incoming connection, will call
either the \texttt{RequestHandler} or \texttt{RackHandler} depending on
whether a Rack application is loaded or not. Listing~\ref{worker_loop}
displays the loop run in each worker process.

\newpage
\begin{lstlisting}[label=worker_loop,caption=Worker loop
(Yarn/lib/yarn/server.rb:90)]
loop do
  @session = @socket.accept
  configure_socket
  handler.run @session
end
\end{lstlisting}

For each iteration the loop will wait at line 2 for an incoming connection,
and not busy-wait and run again. Once a connection is registered, the socket
is configured with some TCP optimizations and then the supplied to the
instantiated handler. The handler classes takes care of all the
rest and closes the connection when finished. If the user sends
the interrupt signal (usually by pressing Ctrl-c), Yarn will kill the worker
processes, close the TCP server and exit.
